---
title: "How to create class repos"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to create class repos}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", eval = FALSE
)
```

```{r setup}
library(github335)
library(tidyverse)
library(googlesheets4)
library(gh)
library(stringr)
library(RVerbalExpressions)
```

## Setting Up

First we will need to define a few variables that will help us when we are using the functions below.

```{r}
semester_id <- "Test20" # fa20, sp20, wi20
creator_email <- "hathawayj@gmail.com" # The email that has access to google docs.

semester_name <- str_c("student_", semester_id)
ta_name <- str_c("ta_", semester_id)
semester_id_upper <- str_to_upper(semester_id)

google_sheet_githubnames <- "https://docs.google.com/spreadsheets/d/1TB_adLB9cNopQo0JLXfaCxtBW7abibIEmqYopqT-AAI/edit?usp=sharing"

```


## Creating cohort information

First create the ta and the student group for the semester. Then get the GitHub ids for each team.

```{r}
dwv_create_groups(semester_name = semester_name, ta_name = ta_name) 

teams <- dwv_get_teams(semester_name = semester_name, ta_name = ta_name) 

students_team_id <- pull(teams, students_team_id)

ta_team_id <- pull(teams, ta_team_id)
```

## Updating with one new student

We assume that a tibble object is created for the new student and that all groups have been created for the current semester.


```{r}
one_student <- structure(list(Student = "J Hathaway", `BYUI Email` = "hathawayj@byui.edu", 
    gitName = "hathawayj", description = "MCS 335 TEST repository for J Hathaway coursework", 
    has_ghname = TRUE, name = "M335_TEST20_Hathaway_J"), class = c("tbl_df", 
"tbl", "data.frame"), row.names = c(NA, -1L))
```

 - **Student:** Their name in First Last format with a space between first and last.
 - **BYUI Email:** A BYU-I email. Although not used much in the process so it can be empty.
 - **gitName:** The github username.
 - **description:** The description you want to use with the new repo. Currently 'MCS 335 repository for [NAME] coursework'
 - **has_ghname:**
 - **name:** The name of the github repo. Currently of this format. 'M335_SP20_[LASTNAME]_[FIRSTFEWOFFIRSTNAME]' 

|Student    |BYUI Email         |gitName   |description                                  |has_ghname |name                 |
|:----------|:------------------|:---------|:--------------------------------------------|:----------|:--------------------|
|J Hathaway |hathawayj@byui.edu |hathawayj |MCS 335 repository for J Hathaway coursework |TRUE       |M335_SP20_Hathaway_J |


**Creating Issues:** If you are using GitHub for the students to manage their progress then you will need to create issues and push the tasks into them. It is built to pull information from an md file of the [following format](https://byuistats.github.io/M335/tasklist.md). 

Use the wrapper `dwv_one_student()` function with the `body_lines` argument set to `NULL` and no issues will be created for the student.

```{r}

body_lines = read_lines("https://byuistats.github.io/M335/tasklist.md")

```



```{r}
dwv_one_student(one_student = one_student, class_group = "student_Test20",
                ta_group = "ta_Test20", body_lines = body_lines)

# You can delete a repo using the following commented function
# dwv_delete_github("M335_Test20_Hathaway_J")
  
```

```{r, echo=FALSE}
dwv_delete_github("M335_TEST20_Hathaway_J")
```

The `dwv_one_student()` function simply works throught the following functions in the package in the order listed.  You can run them individually if you prefer.


```{r}

dwv_check_names(one_student)
dwv_check_repos(one_student)

dwv_copy_repo(one_student$name, one_student$description)
team_ids <- dwv_get_teams(semester_name = "student_Test20", ta_name = "ta_Test20") 

dwv_invite_group(one_student, pull(team_ids,students_team_id))
dwv_add_student(one_student)
dwv_add_group(one_student, "pull", pull(team_ids, students_team_id))
dwv_add_group(one_student, "admin", pull(team_ids, ta_team_id))
dwv_remove_watching(one_student) # run authenticad as user.
dwv_team_repos(pull(team_ids, students_team_id))

dwv_issue_cs(body_lines, dat = one_student)
dwv_issue_tasks(body_lines, dat = one_student)
dwv_issue_semester(body_lines, dat = one_student)

```


```{r, echo=FALSE}
dwv_delete_github("M335_TEST20_Hathaway_J")
```


## Moving through a tibble of students

The following code examples use `purrr` to move through a full table of students.

### Creating Student Repos

First, we need to have the table of student emails and GitHub usernames. It is hard coded to use the google sheet column names above.

```{r}
#drive_auth(email = creator_email)
gs4_auth(email = creator_email)
mdf <- read_sheet(google_sheet_githubnames, sheet = semester_id_upper) %>%
  mutate(Name = Name %>% str_trim() %>% str_remove_all("\\."),
    `BYUI Email` = str_to_lower(`BYUI Email`) %>%
      str_replace_all(rx() %>%
                        rx_find("@") %>%
                        rx_anything() %>%
                        rx_end_of_line(), "@byui.edu")) %>%
  select(Student = Name, `BYUI Email`, gitName = `GitHub Username`)

```

Then we have to check if their GitHub username exists.

```{r}
check_names <- dwv_check_names(mdf)
has_ghname <- check_names$has_ghname
git_students <- check_names$git_students
```

Now we build the table to create student repositories and check to see if the repos are created.


```{r}
## prepare a data frame to drive repo creation
repo_create_df <- mdf %>%
  mutate(description = paste("MCS 335 repository for", Student, "coursework"),
         has_ghname = has_ghname,
         # a bunch of code to build a repo id for each student
         name = str_c("M335_", semester_id_upper, "_",
                      Student %>% 
                        str_split_fixed(" ", 2) %>% 
                        .[,2] %>% 
                        str_replace_all(" ", "_"),
                      "_",
                      Student %>% 
                        str_split_fixed(" ", 2) %>% .[,1] %>% str_sub(1,4),
                      sep = ""))

oops <- dwv_check_repos(repo_create_df)

```

Now we create the GitHub repos for the new students that don't have a repository in their name and have a github username. 

```{r}
# 
(repo_create_df_new <- repo_create_df %>% filter(has_ghname & oops))

## This makes the repositories for each student

# purrr::map(repo_create_df_new$name, dwv_delete_github)

res <- purrr::map2(repo_create_df_new$name, repo_create_df_new$description, dwv_copy_repo)

# this just makes sure the repos were created.
status <- repo_create_df_new %>%
  mutate(cr_success = map_lgl(transpose(res)$result, Negate(is.null))) %>%
  select(-description)

```

### Sharing and Permissions 

Now invite the students to the team for this semester's class. The student group only has read permissions.

**You will need to invite the TAs to the ta group manually**. Currently done manually [here](https://github.com/orgs/BYUI335/teams). The TAs have read/write privileges.  

```{r}
# invites students into the class semester group
dwv_invite_group(repo_create_df_new, students_team_id)

# Gives student read/write access to their repo.
dwv_add_student(repo_create_df_new)

# Adds class group to all the student repos for the semester
dwv_add_group(repo_create_df_new, "pull", students_team_id)

# Adds the TA group to all the repos for the semester
dwv_add_group(repo_create_df_new, "admin", ta_team_id)

# removes the teacher or creator from getting emails.
dwv_remove_watching(repo_create_df_new) # run authenticad as user.

## look at all the repos associated with this team
dwv_team_repos(students_team_id)
```

### Creating Issues

If you are using GitHub for the students to manage their progress then you will need to create issues and push the tasks into them. It is built to pull informatin from an md file of the [following format](https://byuistats.github.io/M335/tasklist.md).


```{r}
body_lines = read_lines("https://byuistats.github.io/M335/tasklist.md")
```


The below code will push issues to each repository provided in the tibble. Run them in the following order to get the issues to show up in a clean viewable order.

```{r}
# Create the case study (cs) issues. One for each case study
dwv_issue_cs(body_lines, dat = repo_create_df_new)

# Create one issue with all of the class task project tasks in it.
dwv_issue_tasks(body_lines, dat = repo_create_df_new)

# Create one issue with all the semester level items.  Leadership, cover letter
dwv_issue_semester(body_lines, dat = repo_create_df_new)

```


```{r, echo=FALSE}
dwv_delete_github("M335_TEST20_Hathaway_J")
```











